Democratic Algorithm: A Novel Approach to Hierarchical Swarm Intelligence\\

### 2020-09-28 VLSID/paper.tex
Draft_2

\begin{abstract}
Computational intelligence has produced nature inspired algorithms as the new and popular problem solving tool in multi-objective optimization problems. In this paper we present Democratic Algorithm (DA), a social-construct based algorithm heavily inspired from hierarchy swarm intelligence and real life social establishments. Each candidate is given an equal opportunity to take a key role in the decision making process. Additional enhancements such as dynamism and memory retention capabilities boost the performance of DA. A comprehensive study is conducted with 21 benchmark functions to act as proof-of-concept and lay the groundwork for future works. The results so obtained, cement the competence of DA as it outperforms other algorithms in multiple unimodal and multimodal functions.
% diverse fields such as soft computing, functional optimization, data science and machine learning. These algorithms can be further sub-divided, with swarm intelligence, physics-inspired, social, evolutionary algorithms a few noteworthy. In this paper we present Democratic Algorithm (DA) , a social-construct based algorithm heavily inspired from hierarchy swarm intelligence and real life social establishments. Our proposal extends the existing methodology for hierarchical structures by framing experience into a viable component for future applications. A comprehensive study is conducted with 16 benchmark functions and real-life data to cement the competence of the algorithm with DA providing a markup of 2-7.4X of convergence rate. 
\end{abstract}

@@

\begin{align}
\label{eqn:1}
Maximize/Minimize:f\textsubscript{m}(x)& &  m = 1,2\dots,M \\
constraints:g\textsubscript{j}(x) \ge 0& & j=1,2\dots,J \nonumber\\
h\textsubscript{k}(x) = 0& & k=1,2\dots,K \nonumber\\
x\textsubscript{i}\textsuperscript{L} \le x\textsubscript{i} \le x\textsubscript{i}\textsuperscript{U} && i = 1,2\dots,n.\nonumber 
\end{align}

Equation $\ref{eqn:1}$ describes a general MOOP consisting of $\textit{M}$ single-objective functions having $\textit{K}$ equality bounds and $\textit{J}$ inequality bounds \cite{chankong}. The $\textit{n}$ input vector components $\textit{x\textsubscript{i}}$ are also bounded within a lower $\textit{x\textsubscript{i}\textsuperscript{L}}$ and upper $\textit{x\textsubscript{i}\textsuperscript{U}}$ bound.

@@

In this section, we provide a brief overview of methods to solve MOOPs and obtain Pareto-optimal solutions. Historically, these methods can be classified into classical and evolutionary techniques. Additional information about these techniques and their sub-classifications are provided in Table $\ref{tab1}$ and $\ref{tab2}$. Every algorithm is set back in one way or the other due to the No Free Lunch Theorem. Our goal in this paper is not create an algorithm which works perfectly for all problems, but to put forth a novel construct which mitigates the drawbacks of it's predecessors.

\begin{table*}[!b]
\caption{\textsc{Classical Solving Methods}}
\label{tab1}
\centering
\scalebox{0.9}
{
\begin{tabular}{| c | c | c | c |}
\hline
\textbf{Subclass} & \textbf{Optimization Equation} & \textbf{Advantages} & \textbf{Disdvantages}\\
\hline
 &&&\\
 Weighting Method & $F\textsubscript{m}(x) =  \sum_{m=1}^{M}w\textsubscript{m}f\textsubscript{m}(x)$ & Simple, Intuitive & No constraints on weights, Not optimal for \\
 &&&nonconvex problems, Interactive\\
\hline
&&&\\
 $\epsilon$-Contrainst Method & $F\textsubscript{l}(x)$ w.r.t $F\textsubscript{m}(x) \leq \epsilon\textsubscript{m}$ & Ensures Pareto optimality and uniqueness,  & Not scalable, Range requirement,\\
   &  & Convexity is not necessary & Interactive \\
 &&&\\
 \hline 
 Neutral Compromise Solution & $\frac{F\textsubscript{m}(x) - ((z\textsubscript{i}\textsuperscript{*} + z\textsubscript{i}\textsuperscript{nad})/2)}{z\textsubscript{i}\textsuperscript{nad} - z\textsubscript{i}\textsuperscript{*}}$ & Approximate Solution, Rapid Process  & Weakly Pareto, Utopian and  \\
  &  &  & Nadir solution required \\
\hline
 Weighted Metrics & $(\sum_{m=1}^{M}w\textsubscript{m}|f\textsubscript{m}(x) - z\textsubscript{m}\textsuperscript{*}|\textsuperscript{p})\textsuperscript{\sufr{1}{p}}$ & Smaller feasible region & Nondifferentiable in some cases, \\
  &  &  & Convexity is required\\
 \hline
 &&&\\
 Value Function Method & $\mathbb{U}(F(x))$ & Excellent results when & Mandatory and Over simplified\\
   &  & mathematical representation is provided & mapping\\
 &&&\\
 \hline
\end{tabular}
}
\end{table*}

\begin{table*}[!b]
\caption{\textsc{Evolutionary Solving Methods}}
\label{tab2}
\centering

{
\begin{tabular}{| c | c | c |}
\hline
\textbf{Subclass}&\textbf{Advantages}&\textbf{Disadvantage}\\
\hline
Preference relation&Dominant Pareto guarentee&Required reference point\\
\hline
Light Beam Method&Optimal distance crowding&Reference direction threshold\\
\hline
Imprecise value function&Solution based ranking&Dominant solutions\\
\hline
Biased Crowding&Desired trade-off&Crowding of solutions\\
\hline
\end{tabular}
}
\end{table*}

@@

From a mathematical point of view, both the structure and the search processes evolve over time with feedback. For each search, a lookup is conducted by candidate $\textit{c}$ in table $\textit{H}$. If not found, a solution $\textit{x\textsubscript{0}}$ is assumed as the initial point and the search of optimum solution $\textit{x\textsubscript{1}}$. To escape the local optimum, a penalty is added to the fitness function $\textit{f}$ such that the resulting fitness function h allows local search to escape. A new local search is started from $\textit{x\textsubscript{1}}$ using the modified fitness function $\textit{f}$. Search continues until a termination criterion is met. Based on the representation, the following observations can be made:
\begin{itemize}
\item The updation process occurs at an individual and departmental level to save the best solutions obtained so far
\item The parameters $\vec{A}$ and $\vec{C}$ assist the solutions to have higher dimensionality
\item Due to the dual updation and introduction of a memory element, the problems functions will saturate at a middle level department
\item The voting season provides weighted rights to each candidate in each department. The weights are assigned based on the individual's fitness which in turn is dependent on their department's position 
\item As the department rank increases, the number of individual candidate in the department decreases to promote elitism. This would ensure survival of the best solutions in future problems. 
\item As the department rank decreases, the number of individual candidate in the department increase to promote diversity. This would open up new avenues to explore and possibly increase chances of finding the gobal optimum.  
\item The increased number of parameters requires fine tunning which can be automated
\end{itemize}

@@

\begin{table*}[!t]
\caption{\textsc{Benchmark Functions}}
\label{tab:1}
\centering
\scalebox{0.9}
{
\begin{tabular}{| >{\arraybackslash}m{0.88in} | c | c | >{\arraybackslash}m{0.4in} | c | >{\arraybackslash}m{1in} | c |}
\hline
Function & ID & Formula & Modality & Range & Minimum Value & Department \\
\hline
Matyas & F1 & $0.26(x\textsubscript{2} + y\textsubscript{2}) - 0.48xy$ & Uni & [-10,10] & 0 at $x\textsuperscript{*}$ = (0,0) & A\\
Booth & F2 & $(x + 2y - 7)\textsuperscript{2} + (2x + y - 5)\textsuperscript{2}$ & Uni & [-10,10] & 0 at $x\textsuperscript{*}$ = (1,3) & A\\
Bohachevsky & F3 & $x\textsuperscript{2} + 2y\textsuperscript{2} -0.3cos(3\pi x)-0.4cos(4\pi y)+0.7$ & Uni & [-100,100] & 0 at $x\textsuperscript{*}$ = (0,0) & A\\
Gramacy and Lee & F4 & $\frac{sin(10\pi x)}{2x} + (x-1)\textsuperscript{4}$ & Uni & [-0.5,2.5] & -0.869 at $x\textsuperscript{*}$ = (0.5485) & A\\
Leon & F5 & $100(y-x\textsuperscript{3})\textsuperscript{2}$ + $(1-x)\textsuperscript{2}$ & Uni & [-10,10] & 0 at $x\textsuperscript{*}$ = (1,1) & B\\
Ackley & F6 & $-20 exp(-0.2 \sqrt{\frac{1}{n} \sum_{i=1}^n x_i^2}) - exp(\frac{1}{n} \sum_{i=1}^n cos(2\pi x_i)) + 20 + e$ & Multi & [-32,32] & 0 at $x\textsuperscript{*}$ = (0,0) & A\\
Bartels & F7 & $|x\textsuperscript{2} + y\textsuperscript{2} + xy| + |sin(x)| + |cos(y)|$ & Multi & [-500,500], [-500,500] & 1 at $x\textsuperscript{*}$ = (0,0) & A\\
Branin & F8 & $a(x\textsubscript{2} - bx\textsubscript{1}\textsuperscript{2} + cx\textsubscript{1} - r)\textsuperscript{2}$ + $s(1-t)cos(x\textsubscript{1})$ + s & Multi & [-5,10], [0,15] & 0.397887 at $x\textsuperscript{*}$ = (-$\pi$, 12.275) & B\\
Egg Crate & F9 & $x\textsuperscript{2}$ + $y\textsuperscript{2}$ + $25(sin\textsuperscript{2}(x) + cos\textsuperscript{2}(x))$ & Multi & [-5,5] & 0 at $x\textsuperscript{*}$ = (0,0) & B\\
Qing & F10 & $\sum_{i=1}^{n}(x^2-i)^2$ & Multi & [-500,500] & 0 at $x\textsuperscript{*}$ = ($\pm\sqrt{i}$) & A\\
Rastrigin & F11 & $10n + \sum_{i=1}^{n}(x_i^2 - 10cos(2\pi x_i))$ & Multi & [-5.12,5.12], [-500,500] & 0 at $x\textsuperscript{*}$ = (0,0) & C\\
Rosenbrock & F12 & $\sum_{i=1}^{n}[b (x_{i+1} - x_i^2)^ 2 + (a - x_i)^2]$ & Multi & [-5.12,5.12], [-5,10] & 0 at $x\textsuperscript{*}$ = (1) & C\\
Bird & F13 & $sin(x)e\textsuperscript{(1-cos(y))^2}+cos(y)e\textsuperscript{(1-sin(x))^2}+(x-y)\textsubscript{2}$ & Multi & [-2$\pi$, 2$\pi$] & -106.76 at $x\textsuperscript{*}$ = (4.70104,3.1529), (-1.58214,-3.1302) & A\\
Powell Sum & F14 & $\sum_{i=1}^{n}|x_i|^{i+1}$ & Multi & [-1,1] & 0 at $x\textsuperscript{*}$ = 0 & A\\
Schaffer & F15 & $0.5 + \frac{sin\textsuperscript{2}(x\textsuperscript{2}-y\textsuperscript{2})-0.5}{(1+0.001(x\textsuperscript{2}+x\textsuperscript{2}))\textsuperscript{2}}$ & Multi & [-100,100] & 0 at $x\textsuperscript{*}$ = (0,0) & B\\
Shubert & F16 & $\prod_{i=1}^{n}{\left(\sum_{j=1}^5{ cos((j+1)x_i+j)}\right)}$ & Multi & [-10,10] & -186.7309  & A\\
Happy Cat & F17 & $\left[\left(||\textbf{x}||^2 - n\right)^2\right]^\alpha + \frac{1}{n}\left(\frac{1}{2}||\textbf{x}||^2+\sum_{i=1}^{n}x_i\right)+\frac{1}{2}$ & Multi & [-2,2] & 0 at $x\textsuperscript{*}$ = (-1)  & A\\
Alpine & F18 & $\prod_{i=1}^{n}\sqrt{x_i}sin(x_i)$ & Multi & [0,10] & 2.808 at $x\textsuperscript{*}$ = (7.917)  & B\\
\hline
\end{tabular}
}
\end{table*}

\begin{table*}[t]
\caption{\textsc{Benchmark Results}}
\label{tab:2}
\centering
{
\begin{tabular}{| c | c  c | c  c | c  c | c  c | c  c |}
\hline
{\textbf{Function}}&{\textbf{PSO}}&{}&{\textbf{GWO}}&{}&{\textbf{MVO}}&{}&{\textbf{CS}}&{}&{\textbf{DA}}&{}\\
\hline
{}&{\textbf{Mean}}&{\textbf{Std}}&{\textbf{Mean}}&{\textbf{Std}}&{\textbf{Mean}}&{\textbf{Std}}&{\textbf{Mean}}&{\textbf{Std}}&{\textbf{Mean}}&{\textbf{Std}}\\
\hline
{F1}&{1.339E-08}&{6.224E-04}&{2.411E-06}&{4.968E-05}&{5.221E-06}&{8.235E-08}&{9.711E-06}&{4.397E-07}&{8.712E-06}&{5.113E-05}\\
{F2}&{4.859E-10}&{0.5287}&{6.276E-09}&{5.171E-06}&{6.181E-07}&{0.8412}&{9.551E-09}&{3.854E-07}&{7.622E-11}&{2.625E-06}\\
{F3}&{8.156E-13}&{1.712E-07}&{3.897E-11}&{8.422E-07}&{9.252E-15}&{4.976E-06}&{2.416E-12}&{8.256E-07}&{1.823E-15}&{7.424E-05}\\
{F4}&{-0.7624}&{3.153}&{-0.6887}&{18.542}&{-0.8219}&{12.843}&{-0.7943}&{28.954}&{-0.8149}&{21.148}\\
{F5}&{0}&{0.0133}&{5.18E-24}&{0.0023}&{4.81E-20}&{0.0141}&{5.73E-27}&{0.0072}&{8.19E-29}&{0.0058}\\
{F6}&{5.177E-16}&{0.0251}&{1.415E-11}&{0.0595}&{2.478E-38}&{0.0224}&{7.714E-24}&{0.0119}&{4.082E-32}&{0.0084}\\
{F7}&{0.9521}&{0.0253}&{0.8445}&{0.0081}&{0.5122}&{0.0047}&{0.9154}&{0.0005}&{0.9204}&{0.0007}\\
{F8}&{0.3181}&{0.0012}&{0.2118}&{0.0084}&{0.3518}&{0.0152}&{0.3154}&{0.0002}&{0.3751}&{0.0084}\\
{F9}&{1.145E-08}&{5.152E-06}&{1.845E-09}&{5.691E-05}&{4.845E-08}&{3.452E-06}&{7.183E-08}&{6.541E-07}&{2.495E-09}&{5.88E-06}\\
{F10}&{5.483E-19}&{4.465E-08}&{7.842E-18}&{9.421E-05}&{7.515E-25}&{4.118E-05}&{9.152E-19}&{4.783E-05}&{1.215E-19}&{2.512E-06}\\
{F11}&{6.152E-20}&{0.0512}&{4.125E-38}&{0.0001}&{2.489E-28}&{0.0915}&{4.852E-26}&{0.0185}&{4.845E-29}&{0.0943}\\
{F12}&{0.0051}&{0.0218}&{0.0009}&{0.3512}&{0.0205}&{0.0945}&{0.0006}&{0.1534}&{0.001}&{0.0035}\\
{F13}&{-100.15}&{0.0029}&{-98.153}&{0.0675}&{-63.156}&{0.0005}&{-156.51}&{0.0266}&{-94.845}&{0.432}\\
{F14}&{0.0241}&{0.0008}&{0.0099}&{0.0021}&{0.0007}&{0.0315}&{0.0842}&{0.0239}&{0.0579}&{0.0679}\\
{F15}&{5.194E-16}&{8.495E-05}&{7.162E-20}&{2.846E-05}&{7.899E-E11}&{3.793E-05}&{6.977E-19}&{8.297E-05}&{3.842E-22}&{2.655E-07}\\
{F16}&{-215.15}&{0.0021}&{-288.31}&{0.0842}&{-160.249}&{0.3512}&{-206.49}&{0.0002}&{-153.123}&{0.0004}\\
{F17}&{0.0021}&{0.1532}&{0.0044}&{0.2953}&{0.0531}&{0.0212}&{0.0094}&{0.0121}&{0.0076}&{0.4683}\\
{F18}&{2.5321}&{0.0515}&{1.2854}&{0.7542}&{1.9458}&{0.1523}&{2.0057}&{0.0021}&{2.6185}&{0.0218}\\
\hline
\end{tabular}
}
\end{table*}

@@

\begin{figure}[htp]
  \centering
  \label{figur}\caption{Department A Dominant}

@@

\begin{figure}[htp]
  \centering
  \label{figur}\caption{Department B Dominant}

@@

\begin{figure*}[htp]
  \centering
  \label{figur}\caption{Department C Dominant}

@@

\begin{itemize}
\item Improved updation rules for the coefficient vectors.
\item Increase the number of parameters for improved model performance.
\item Generate a framework to decide on the number of departments.
\item Decrease the complexity of the algorithm by improving the table updation.
\item Introduction of concurrency.
% This document is a model and instructions for \LaTeX.
% Please observe the conference page limits. 
% 
% \section{Ease of Use}
% 
% \subsection{Maintaining the Integrity of the Specifications}
% 
% The IEEEtran class file is used to format your paper and style the text. All margins, 
% column widths, line spaces, and text fonts are prescribed; please do not 
% alter them. You may note peculiarities. For example, the head margin
% measures proportionately more than is customary. This measurement 
% and others are deliberate, using specifications that anticipate your paper 
% as one part of the entire proceedings, and not as an independent document. 
% Please do not revise any of the current designations.
% 
% \section{Prepare Your Paper Before Styling}
% Before you begin to format your paper, first write and save the content as a 
% separate text file. Complete all content and organizational editing before 
% formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
% proofreading, spelling and grammar.
% 
% Keep your text and graphic files separate until after the text has been 
% formatted and styled. Do not number text heads---{\LaTeX} will do that 
% for you.
% 
% \subsection{Abbreviations and Acronyms}\label{AA}
% Define abbreviations and acronyms the first time they are used in the text, 
% even after they have been defined in the abstract. Abbreviations such as 
% IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
% abbreviations in the title or heads unless they are unavoidable.
% 
% \subsection{Units}
% \begin{itemize}
% \item Use either SI (MKS) or CGS as primary units. (SI units are encouraged.) English units may be used as secondary units (in parentheses). An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
% \item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds. This often leads to confusion because equations do not balance dimensionally. If you must use mixed units, clearly state the units for each quantity that you use in an equation.
% \item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''. Spell out units when they appear in text: ``. . . a few henries'', not ``. . . a few H''.
% \item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
% \end{itemize}
% 
% \subsection{Equations}
% Number equations consecutively. To make your 
% equations more compact, you may use the solidus (~/~), the exp function, or 
% appropriate exponents. Italicize Roman symbols for quantities and variables, 

>>>>

\begin{abstract}
Computational intelligence has produced nature inspired algorithms as the new and popular problem solving tool in multi-objective optimization problems. In this paper we present Democratic Algorithm (DA), a social-construct based algorithm heavily inspired from hierarchy swarm intelligence and real life social establishments. Each candidate in the swarm takes part in the search process and contends for the position of the leader. Additional enhancements such as dynamism and memory retention capabilities boost the performance of DA. A comprehensive study is conducted with 21 benchmark functions to act as proof-of-concept and lay the groundwork for future works. The results so obtained, cement the competence of DA as it outperforms other algorithms in multiple unimodal and multimodal functions.
% diverse fields such as soft computing, functional optimization, data science and machine learning. These algorithms can be further sub-divided, with swarm intelligence, physics-inspired, social, evolutionary algorithms a few noteworthy. In this paper we present Democratic Algorithm (DA) , a social-construct based algorithm heavily inspired from hierarchy swarm intelligence and real life social establishments. Our proposal extends the existing methodology for hierarchical structures by framing experience into a viable component for future applications. A comprehensive study is conducted with 16 benchmark functions and real-life data to cement the competence of the algorithm with DA providing a markup of 2-7.4X of convergence rate. 
\end{abstract}

@@

{\scriptsize
\begin{align}
\label{eqn:1}
Maximize/Minimize:f\textsubscript{m}(x)& &  m = 1,2\dots,M \\
constraints:g\textsubscript{j}(x) \ge 0& & j=1,2\dots,J \nonumber\\
h\textsubscript{k}(x) = 0& & k=1,2\dots,K \nonumber\\
x\textsubscript{i}\textsuperscript{L} \le x\textsubscript{i} \le x\textsubscript{i}\textsuperscript{U} && i = 1,2\dots,n.\nonumber 
\end{align}
}%
Equation $\ref{eqn:1}$ describes a general MOOP consisting of $\textit{M}$ single-objective functions having $\textit{K}$ equality bounds and $\textit{J}$ inequality bounds \cite{chankong}. The $\textit{n}$ input vector components $\textit{x\textsubscript{i}}$ are also bounded within a lower $\textit{x\textsubscript{i}\textsuperscript{L}}$ and upper $\textit{x\textsubscript{i}\textsuperscript{U}}$ bound.

@@

In this section, we provide a brief overview of methods to solve MOOPs and obtain Pareto-optimal solutions. Historically, these methods can be classified into classical and evolutionary techniques \cite{vikhar} \cite{swarm}. Additional information about these techniques and their sub-classifications are provided in Table $\ref{tab1}$ and $\ref{tab2}$. Every algorithm is set back in one way or the other due to the No Free Lunch Theorem. Our goal in this paper is not create an algorithm which works perfectly for all problems, but to put forth a novel construct which mitigates the drawbacks of it's predecessors.

\begin{table*}
\caption{\textsc{Classical Solving Methods}}
\label{tab1}
\centering
\scalebox{0.9}
{
\begin{tabular}{| c | c | c | c |}
\hline
\textbf{Subclass} & \textbf{Optimization Equation} & \textbf{Advantages} & \textbf{Disdvantages}\\
\hline
 &&&\\
 Weighting Method \cite{arora} & $F\textsubscript{m}(x) =  \sum_{m=1}^{M}w\textsubscript{m}f\textsubscript{m}(x)$ & Simple, Intuitive & No constraints on weights, Not optimal for \\
 &&&nonconvex problems, Interactive\\
\hline
&&&\\
 $\epsilon$-Contrainst Method \cite{cooper}& $F\textsubscript{l}(x)$ w.r.t $F\textsubscript{m}(x) \leq \epsilon\textsubscript{m}$ & Ensures Pareto optimality and uniqueness,  & Not scalable, Range requirement,\\
   &  & Convexity is not necessary & Interactive \\
 &&&\\
 \hline 
 Neutral Compromise Solution & $\frac{F\textsubscript{m}(x) - ((z\textsubscript{i}\textsuperscript{*} + z\textsubscript{i}\textsuperscript{nad})/2)}{z\textsubscript{i}\textsuperscript{nad} - z\textsubscript{i}\textsuperscript{*}}$ & Approximate Solution, Rapid Process  & Weakly Pareto, Utopian and  \\
  &  &  & Nadir solution required \\
\hline
 Weighted Metrics \cite{ryu}& $(\sum_{m=1}^{M}w\textsubscript{m}|f\textsubscript{m}(x) - z\textsubscript{m}\textsuperscript{*}|\textsuperscript{p})\textsuperscript{\sufr{1}{p}}$ & Smaller feasible region & Nondifferentiable in some cases, \\
  &  &  & Convexity is required\\
 \hline
 &&&\\
 Value Function Method \cite{sinha}& $\mathbb{U}(F(x))$ & Excellent results when & Mandatory and Over simplified\\
   &  & mathematical representation is provided & mapping\\
 &&&\\
 \hline
\end{tabular}
}
\end{table*}

\begin{table*}

\caption{\textsc{Evolutionary Solving Methods}}
\label{tab2}
\centering
% \scalebox{0.9}
{
\begin{tabular}{| c | c | c |}
\hline
\textbf{Subclass}&\textbf{Advantages}&\textbf{Disadvantage}\\
\hline
Preference relation \cite{kim}&Dominant Pareto guarentee&Required reference point\\
\hline
Light Beam Method \cite{an}&Optimal distance crowding&Reference direction threshold\\
\hline
Imprecise value function \cite{lim}&Solution based ranking&Dominant solutions\\
\hline
Biased Crowding&Desired trade-off&Crowding of solutions\\
\hline
\end{tabular}
}
\end{table*}

@@

From a mathematical point of view, both the structure and the search processes evolve over time with feedback. For each search, a lookup is conducted by candidate $\textit{c}$ in table $\textit{H}$. If not found, a solution $\textit{x\textsubscript{0}}$ is assumed as the initial point and the search of optimum solution $\textit{x\textsubscript{1}}$ begins. At the end of each expedition, the top department's performance is graded through a reward system. Based on the global performance overall a set runtime, either the department continues in power or gets replaced. Based on the representation, the following observations can be made:
\begin{itemize}
\item The updation process occurs at an individual and at a departmental level to save the best solutions obtained so far
\item The parameters $\vec{A}$ and $\vec{C}$ assist the solutions to have higher dimensionality
\item Due to the dual updation and introduction of a memory element, the problems functions will saturate at a middle level department
\item The voting season provides weighted rights to each candidate in each department. The weights are assigned based on the individual's fitness which in turn is dependent on their department's position 
\item As the department rank increases, the number of individual candidate in the department decreases to promote elitism. This would ensure survival of the best solutions in future problems. 
\item As the department rank decreases, the number of individual candidate in the department increase to promote diversity. This would open up new avenues to explore and possibly increase chances of finding the gobal optimum.  
\item The increased number of parameters requires fine tunning which can be automated
\end{itemize}

@@

\begin{table*}
\caption{\textsc{Benchmark Functions}}
\label{tab:1}
\centering
\scalebox{0.9}
{
\begin{tabular}{| >{\arraybackslash}m{0.88in} | c | c | >{\arraybackslash}m{0.4in} | c | >{\arraybackslash}m{1in} | c |}
\hline
Function & ID & Formula & Modality & Range & Minimum Value & Department \\
\hline
Matyas & F1 & $0.26(x\textsubscript{2} + y\textsubscript{2}) - 0.48xy$ & Uni & [-10,10] & 0 at $x\textsuperscript{*}$ = (0,0) & A\\
Booth & F2 & $(x + 2y - 7)\textsuperscript{2} + (2x + y - 5)\textsuperscript{2}$ & Uni & [-10,10] & 0 at $x\textsuperscript{*}$ = (1,3) & A\\
Bohachevsky & F3 & $x\textsuperscript{2} + 2y\textsuperscript{2} -0.3cos(3\pi x)-0.4cos(4\pi y)+0.7$ & Uni & [-100,100] & 0 at $x\textsuperscript{*}$ = (0,0) & A\\
Gramacy and Lee & F4 & $\frac{sin(10\pi x)}{2x} + (x-1)\textsuperscript{4}$ & Uni & [-0.5,2.5] & -0.86 at $x\textsuperscript{*}$ = (0.54) & A\\
Leon & F5 & $100(y-x\textsuperscript{3})\textsuperscript{2}$ + $(1-x)\textsuperscript{2}$ & Uni & [-10,10] & 0 at $x\textsuperscript{*}$ = (1,1) & B\\
Ackley & F6 & $-20 exp(-0.2 \sqrt{\frac{1}{n} \sum_{i=1}^n x_i^2}) +$ e + & Multi & [-32,32] & 0 at $x\textsuperscript{*}$ = (0,0) & A\\
& &20 - $exp(\frac{1}{n} \sum_{i=1}^n cos(2\pi x_i))$&&&&\\
Bartels & F7 & $|x\textsuperscript{2} + y\textsuperscript{2} + xy| + |sin(x)| + |cos(y)|$ & Multi & [-500,500], [-500,500] & 1 at $x\textsuperscript{*}$ = (0,0) & A\\
Branin & F8 & $a(x\textsubscript{2} - bx\textsubscript{1}\textsuperscript{2} + cx\textsubscript{1} - r)\textsuperscript{2}$ + $s(1-t)cos(x\textsubscript{1})$ + s & Multi & [-5,10], [0,15] & 0.39 at $x\textsuperscript{*}$ = (-$\pi$, 12.275) & B\\
Egg Crate & F9 & $x\textsuperscript{2}$ + $y\textsuperscript{2}$ + $25(sin\textsuperscript{2}(x) + cos\textsuperscript{2}(x))$ & Multi & [-5,5] & 0 at $x\textsuperscript{*}$ = (0,0) & B\\
Qing & F10 & $\sum_{i=1}^{n}(x^2-i)^2$ & Multi & [-500,500] & 0 at $x\textsuperscript{*}$ = ($\pm\sqrt{i}$) & A\\
Rastrigin & F11 & $10n + \sum_{i=1}^{n}(x_i^2 - 10cos(2\pi x_i))$ & Multi & [-5.12,5.12], [-500,500] & 0 at $x\textsuperscript{*}$ = (0,0) & C\\
Rosenbrock & F12 & $\sum_{i=1}^{n}[b (x_{i+1} - x_i^2)^ 2 + (a - x_i)^2]$ & Multi & [-5.12,5.12], [-5,10] & 0 at $x\textsuperscript{*}$ = (1) & C\\
Bird & F13 & $sin(x)e\textsuperscript{(1-cos(y))\textsuperscript{2}}+cos(y)e\textsuperscript{(1-sin(x))\textsuperscript{2}}+(x-y)\textsuperscript{2}$ & Multi & [-2$\pi$, 2$\pi$] & -106.76 at $x\textsuperscript{*}$ = (4.70,3.15),(-1.58,-3.13) & A\\
Powell Sum & F14 & $\sum_{i=1}^{n}|x_i|^{i+1}$ & Multi & [-1,1] & 0 at $x\textsuperscript{*}$ = 0 & A\\
Schaffer & F15 & $0.5 + \frac{sin\textsuperscript{2}(x\textsuperscript{2}-y\textsuperscript{2})-0.5}{(1+0.001(x\textsuperscript{2}+x\textsuperscript{2}))\textsuperscript{2}}$ & Multi & [-100,100] & 0 at $x\textsuperscript{*}$ = (0,0) & B\\
Shubert & F16 & $\prod_{i=1}^{n}{\left(\sum_{j=1}^5{ cos((j+1)x_i+j)}\right)}$ & Multi & [-10,10] & -186.7309  & A\\
Happy Cat & F17 & $\left[\left(||\textbf{x}||^2 - n\right)^2\right]^\alpha + \frac{1}{n}\left(\frac{1}{2}||\textbf{x}||^2+\sum_{i=1}^{n}x_i\right)+\frac{1}{2}$ & Multi & [-2,2] & 0 at $x\textsuperscript{*}$ = (-1)  & A\\
Alpine & F18 & $\prod_{i=1}^{n}\sqrt{x_i}sin(x_i)$ & Multi & [0,10] & 2.80 at $x\textsuperscript{*}$ = (7.91)  & B\\
\hline
\end{tabular}
}
\end{table*}

\begin{table*}
\caption{\textsc{Benchmark Results}}
\label{tab:2}
\centering
{
\begin{tabular}{| c | c  c | c  c | c  c | c  c | c  c |}
\hline
{\textbf{Function}}&{\textbf{PSO}}&{}&{\textbf{GWO}}&{}&{\textbf{MVO}}&{}&{\textbf{CS}}&{}&{\textbf{DA}}&{}\\
\hline
{}&{\textbf{Mean}}&{\textbf{Std}}&{\textbf{Mean}}&{\textbf{Std}}&{\textbf{Mean}}&{\textbf{Std}}&{\textbf{Mean}}&{\textbf{Std}}&{\textbf{Mean}}&{\textbf{Std}}\\
\hline
{F1}&{1.339E-08}&{6.224E-04}&{2.411E-06}&{4.968E-05}&{5.221E-06}&{8.235E-08}&{9.711E-06}&{4.397E-07}&{8.712E-06}&{5.113E-05}\\
{F2}&{4.859E-10}&{0.5287}&{6.276E-09}&{5.171E-06}&{6.181E-07}&{0.8412}&{9.551E-09}&{3.854E-07}&{7.622E-11}&{2.625E-06}\\
{F3}&{8.156E-13}&{1.712E-07}&{3.897E-11}&{8.422E-07}&{9.252E-15}&{4.976E-06}&{2.416E-12}&{8.256E-07}&{1.823E-15}&{7.424E-05}\\
{F4}&{-0.7624}&{3.153}&{-0.6887}&{18.542}&{-0.8219}&{12.843}&{-0.7943}&{28.954}&{-0.8149}&{21.148}\\
{F5}&{0}&{0.0133}&{5.18E-24}&{0.0023}&{4.81E-20}&{0.0141}&{5.73E-27}&{0.0072}&{8.19E-29}&{0.0058}\\
{F6}&{5.177E-16}&{0.0251}&{1.415E-11}&{0.0595}&{2.478E-38}&{0.0224}&{7.714E-24}&{0.0119}&{4.082E-32}&{0.0084}\\
{F7}&{0.9521}&{0.0253}&{0.8445}&{0.0081}&{0.5122}&{0.0047}&{0.9154}&{0.0005}&{0.9204}&{0.0007}\\
{F8}&{0.3181}&{0.0012}&{0.2118}&{0.0084}&{0.3518}&{0.0152}&{0.3154}&{0.0002}&{0.3751}&{0.0084}\\
{F9}&{1.145E-08}&{5.152E-06}&{1.845E-09}&{5.691E-05}&{4.845E-08}&{3.452E-06}&{7.183E-08}&{6.541E-07}&{2.495E-09}&{5.88E-06}\\
{F10}&{5.483E-19}&{4.465E-08}&{7.842E-18}&{9.421E-05}&{7.515E-25}&{4.118E-05}&{9.152E-19}&{4.783E-05}&{1.215E-19}&{2.512E-06}\\
{F11}&{6.152E-20}&{0.0512}&{4.125E-38}&{0.0001}&{2.489E-28}&{0.0915}&{4.852E-26}&{0.0185}&{4.845E-29}&{0.0943}\\
{F12}&{0.0051}&{0.0218}&{0.0009}&{0.3512}&{0.0205}&{0.0945}&{0.0006}&{0.1534}&{0.001}&{0.0035}\\
{F13}&{-100.15}&{0.0029}&{-98.153}&{0.0675}&{-63.156}&{0.0005}&{-156.51}&{0.0266}&{-94.845}&{0.432}\\
{F14}&{0.0241}&{0.0008}&{0.0099}&{0.0021}&{0.0007}&{0.0315}&{0.0842}&{0.0239}&{0.0579}&{0.0679}\\
{F15}&{5.194E-16}&{8.495E-05}&{7.162E-20}&{2.846E-05}&{7.899E-E11}&{3.793E-05}&{6.977E-19}&{8.297E-05}&{3.842E-22}&{2.655E-07}\\
{F16}&{-215.15}&{0.0021}&{-288.31}&{0.0842}&{-160.249}&{0.3512}&{-206.49}&{0.0002}&{-153.123}&{0.0004}\\
{F17}&{0.0021}&{0.1532}&{0.0044}&{0.2953}&{0.0531}&{0.0212}&{0.0094}&{0.0121}&{0.0076}&{0.4683}\\
{F18}&{2.5321}&{0.0515}&{1.2854}&{0.7542}&{1.9458}&{0.1523}&{2.0057}&{0.0021}&{2.6185}&{0.0218}\\
\hline
\end{tabular}
}
\end{table*}

@@

\begin{figure}[!t]
  \centering
  \label{figur}\caption{Department A Dominant}

@@

\begin{figure}[!t]
  \centering
  \label{figur}\caption{Department B Dominant}

@@

\begin{figure*}[!t]
  \centering
  \label{figur}\caption{Department C Dominant}

@@

\begin{itemize}
\item Improved updation rules for the coefficient vectors.
\item Increase the number of parameters for improved model performance.
\item Generate a framework to decide on the number of departments.
\item Decrease the complexity of the algorithm by improving the table updation.
\item Introduction of concurrency.
\end{itemize}
